---
title: "Drill-Down; Pacific vs East South Central"
author: "Nikhil Sharma"
date: "5/15/2020"
output: html_document
---

```{r}
library(tidyverse)
library(questionr)
options(scipen=999)
survey <- read_csv("~/Documents/DataFest-2020/CLEANED_SURVEY_64.csv")
```

#Drill down: East South Central vs. Pacific

Party breakdown per division; visualize dem/repub divide in ESC and Pacific
```{r}
wtd.table(survey$F_PARTYSUM_FINAL, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

East South Central: 53.47% Republican
Pacific: 61.27% Democratic

How would you rate the job Donald Trump is doing responding to the coronavirus outbreak? 
```{r}
pacific <- survey %>% filter(F_CDIVISION == "Pacific")

wtd.table(pacific$COVIDEGFP_a_W64, y = pacific$F_PARTYSUM_FINAL, weights = pacific$WEIGHT_W64) %>% prop.table(margin = 2)
```

```{r}
esc <- survey %>% filter(F_CDIVISION == "East South Central")

wtd.table(esc$COVIDEGFP_a_W64, y = esc$F_PARTYSUM_FINAL, weights = esc$WEIGHT_W64) %>% prop.table(margin = 2)
```


Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable going to a polling place to vote?
```{r}
wtd.table(pacific$COVID_COMFORT_e_W64, y = pacific$F_PARTYSUM_FINAL, weights = pacific$WEIGHT_W64) %>% prop.table(margin = 2)
```

```{r}
wtd.table(esc$COVID_COMFORT_e_W64, y = esc$F_PARTYSUM_FINAL, weights = esc$WEIGHT_W64) %>% prop.table(margin = 2)
```

