---
title: "Pew Explore"
author: "Nikhil Sharma"
date: "5/13/2020"
output: html_document
---

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(questionr)
options(scipen=999)
survey <- read_csv("CLEANED_SURVEY_64.csv")
#View(survey)
```

```{r}
colSums(is.na(survey))
```
F_CREGION, F_AGECAT, F_RACETHN, F_PARTYSUM_FINAL, F_INCOME_RECODE

```{r}
colnames(survey)
```

Would you say the coronavirus outbreak is...
```{r}
wtd.table(survey$COVID_CRISIS_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2) %>% as.data.frame() %>% write.csv("crisis.csv")
```



How would you rate the job each of the following is doing responding to the coronavirus outbreak? 
- Donald Trump
Analysis: In general people think he has performed poorly
```{r}
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How would you rate the job each of the following is doing responding to the coronavirus outbreak? 
- Your state elected officials
Analysis: Netural - pepple are okay with it 
```{r}
wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How would you rate the job each of the following is doing responding to the coronavirus outbreak? 
- Your local elected officials
Analysis: Same as previous one
```{r}
wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How would you rate the job each of the following is doing responding to the coronavirus outbreak? - useless
- Public health officials such as those at the CDC (Centers for Disease Control and Prevention)
```{r}
wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How would you rate the job each of the following is doing responding to the coronavirus outbreak? 
- Ordinary people in your local community
Analysis: Most people are okay with it
```{r}
wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How would you rate the job each of the following is doing responding to the coronavirus outbreak? 
- The news media
Analysis: Democrats are trusting the news generally more. Younger people trust news lesser than older generation
```{r}
wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How much of a threat, if any, is the coronavirus outbreak for...
- The health of the U.S. population as whole
Analysis: More republicans think its not a threat than democrats
```{r}
wtd.table(survey$COVIDTHREAT_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_a_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_a_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_a_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_a_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How much of a threat, if any, is the coronavirus outbreak for...
- Your personal health
Analysis: Old people think its more threatening personally. Democrat and Republic outlook is similar
```{r}
wtd.table(survey$COVIDTHREAT_b_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_b_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_b_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_b_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_b_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How much of a threat, if any, is the coronavirus outbreak for...
- The U.S. economy
Analysis: Everyone thinks its a major threat
```{r}
wtd.table(survey$COVIDTHREAT_c_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_c_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_c_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_c_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_c_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How much of a threat, if any, is the coronavirus outbreak for...
- Your personal financial situation
Analysis: Democrats are more worried, old people don't care, >$75,000 income less worried
```{r}
wtd.table(survey$COVIDTHREAT_d_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_d_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_d_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_d_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDTHREAT_d_W64, y = survey$F_INCOME, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Now, thinking about how different people and groups are reacting to the coronavirus outbreak, how would you say each of the following is reacting?
- Your state government
Analysis: Younger people think state officials could do better, as compared to 65+
```{r}
wtd.table(survey$COVID_STEPS_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_a_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_a_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_a_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_a_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Now, thinking about how different people and groups are reacting to the coronavirus outbreak, how would you say each of the following is reacting?
- Your local government
Analysis: Trend in age same as above
```{r}
wtd.table(survey$COVID_STEPS_b_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_b_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_b_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_b_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_b_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Now, thinking about how different people and groups are reacting to the coronavirus outbreak, how would you say each of the following is reacting?
- Your local school system
Analysis: Everyone is happy with it
```{r}
wtd.table(survey$COVID_STEPS_c_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_c_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_c_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_c_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_c_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Now, thinking about how different people and groups are reacting to the coronavirus outbreak, how would you say each of the following is reacting?
- Ordinary people in your community
Analysis: Young people again are distrustful
```{r}
wtd.table(survey$COVID_STEPS_e_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_e_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_e_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_e_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_e_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Now, thinking about how different people and groups are reacting to the coronavirus outbreak, how would you say each of the following is reacting?
- Ordinary people across the country
Analysis: A large portion of people think poeple are overreacting; young people trust local community more than country
```{r}
wtd.table(survey$COVID_STEPS_f_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_f_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_f_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_f_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_f_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Now, thinking about how different people and groups are reacting to the coronavirus outbreak, how would you say each of the following is reacting?
- The people in your household
Analysis: Happy with it across the board
```{r}
wtd.table(survey$COVID_STEPS_g_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_g_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_g_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_g_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_STEPS_g_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Visiting with a close friend or family member at their home
Analysis: Democrats are less comfortable, young people more comfortable
```{r}
wtd.table(survey$COVID_COMFORT_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_a_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_a_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_a_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_a_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Eating out in a restaurant
Analysis: More republicans are okay with it, more young people are okay with it
```{r}
wtd.table(survey$COVID_COMFORT_b_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_b_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_b_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_b_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_b_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Attending a crowded party
Analysis: Generally people aren't okay with it
```{r}
wtd.table(survey$COVID_COMFORT_c_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_c_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_c_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_c_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_c_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Going out to the grocery store
Analysis: More republicans are okay
```{r}
wtd.table(survey$COVID_COMFORT_d_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_d_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_d_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_d_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_d_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Going to a polling place to vote
Analysis: More Repubilcans
```{r}
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Thinking about some steps that have been announced in some areas to address the coronavirus outbreak, in general do you think each of the
following have been necessary or unnecessary?
- Restricting international travel to the U.S.
Analysis: Everyone doesn't want it
```{r}
wtd.table(survey$COVID_RESTRICTION_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_a_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_a_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_a_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_a_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Thinking about some steps that have been announced in some areas to address the coronavirus outbreak, in general do you think each of the
following have been necessary or unnecessary?
- Requiring most businesses other than grocery stores and pharmacies to close
Analysis: More democrats want things to close than republicans
```{r}
wtd.table(survey$COVID_RESTRICTION_b_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_b_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_b_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_b_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_b_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Thinking about some steps that have been announced in some areas to address the coronavirus outbreak, in general do you think each of the
following have been necessary or unnecessary?
- Asking people to avoid gathering in groups of more than ten
Analysis: Uniform across the board
```{r}
wtd.table(survey$COVID_RESTRICTION_c_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_c_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_c_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_c_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_c_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Thinking about some steps that have been announced in some areas to address the coronavirus outbreak, in general do you think each of the
following have been necessary or unnecessary?
- Cancelling major sports and entertainment events
Analysis: Uniform
```{r}
wtd.table(survey$COVID_RESTRICTION_d_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_d_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_d_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_d_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_d_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Thinking about some steps that have been announced in some areas to address the coronavirus outbreak, in general do you think each of the
following have been necessary or unnecessary?
- Closing K-12 schools
Analysis: Uniform
```{r}
wtd.table(survey$COVID_RESTRICTION_e_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_e_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_e_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_e_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_e_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Thinking about some steps that have been announced in some areas to address the coronavirus outbreak, in general do you think each of the
following have been necessary or unnecessary?
- Limiting restaurants to carry-out only
Analysis: More democrats want take-out only
```{r}
wtd.table(survey$COVID_RESTRICTION_f_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_f_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_f_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_f_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_f_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Thinking about some steps that have been announced in some areas to address the coronavirus outbreak, in general do you think each of the
following have been necessary or unnecessary?
- Postponing upcoming state primary elections
Analysis: More democrats want to postpone, Less in west want to postpone, more younger people want to postpone
```{r}
wtd.table(survey$COVID_RESTRICTION_g_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_g_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_g_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_g_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_g_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

For each of the following, indicate whether or not it is something that happened to YOU OR SOMEONE IN YOUR HOUSEHOLD because of the coronavirus outbreak.
- Been laid off or lost a job
Analysis: more low-income were laid off than high-income, more democrats lost their jobs than republicans
```{r}
wtd.table(survey$COVIDWORK_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDWORK_a_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDWORK_a_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDWORK_a_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDWORK_a_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

For each of the following, indicate whether or not it is something that happened to YOU OR SOMEONE IN YOUR HOUSEHOLD because of the coronavirus outbreak.
- Had to take a cut in pay due to reduced hours or demand for your work
Analysis: more low income had to take a pay cut 
```{r}
wtd.table(survey$COVIDWORK_b_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDWORK_b_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDWORK_b_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDWORK_b_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDWORK_b_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Based on what you have read and heard, what kind of economic impact do you believe that the coronavirus outbreak will have on the United States? - useless
```{r}
wtd.table(survey$COVID_RECESSION_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RECESSION_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RECESSION_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RECESSION_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RECESSION_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How confident, if at all, are you that each of the following will be able to handle the medical needs of people who are seriously ill during the coronavirus
outbreak?
- Hospitals and medical centers in your area
Analysis: More republicans believe so
```{r}
wtd.table(survey$COVID_HEALTHSYS_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_a_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_a_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_a_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_a_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How confident, if at all, are you that each of the following will be able to handle the medical needs of people who are seriously ill during the coronavirus
outbreak?
- Hospitals and medical centers around the country
Analysis: Low confidence across all boards, but more republicans are still more confident
```{r}
wtd.table(survey$COVID_HEALTHSYS_b_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_b_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_b_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_b_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_b_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

How confident, if at all, are you that each of the following will be able to handle the medical needs of people who are seriously ill during the coronavirus
outbreak?
- Nursing homes in your area
Analysis: Low confidence across the board
```{r}
wtd.table(survey$COVID_HEALTHSYS_c_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_c_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_c_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_c_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_HEALTHSYS_c_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```



Have you used social media to share or post information about the coronavirus?
```{r}
wtd.table(survey$F_CDIVISION, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 1)
```


```{r}
survey$F_INCOME <- factor(survey$F_INCOME, levels = c("< 10,000", "10,000 - 20,000", "20,000 - 30,000", "30,000 - 40,000", "40,000 - 50,000", "50,000 - 75,000", "75,000 - 100,000", "100,000 - 150,000", ">150,000"))
```


```{r}
wtd.table(survey$COVIDTHREAT_d_W64, y = survey$F_INCOME, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

```{r}
wtd.table(survey$COVIDTHREAT_d_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```


```{r}
df_income <- wtd.table(survey$COVIDTHREAT_d_W64, y = survey$F_INCOME, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2) %>% as.data.frame() %>% filter (Var1 != "No Response") %>% filter(Var2 != "No Response")
df_income
```

```{r}
df_income$Var2 %>% unique() %>% print()
```




```{r}
df_income$Var2 <- factor(df_income$Var2, levels = c("< 10,000", "10,000 - 20,000", "20,000 - 30,000", "30,000 - 40,000", "40,000 - 50,000", "50,000 - 75,000", "75,000 - 100,000", "100,000 - 150,000", ">150,000"))
```

```{r}
table(df_income$Var1, df_income$Var2)
```


```{r}
ggplot(df_income, aes(x = Var2, y = Freq, group = Var1, color = Var1)) +
  geom_line() +
  ylab("Percentage of Respondents") +
  ggtitle ("How Much of a Threat is the Coronavirus Outbreak on Your Personal Financial Situation?", subtitle = "n = 11,537; Pew Research Center") +
  labs (color = "Threat Level") +
  xlab ("Reported Family Income (USD)") 


```

```{r}
ggplot(df_income, aes(x = Var2, y = Freq, group = Var1, color = Var1)) +
  geom_point() +
  geom_line(size = 1) +
  ylab("Percentage of Respondents") +
  ggtitle ("How Much of a Threat is the Coronavirus Outbreak on Your Personal Financial Situation?", subtitle = "n = 11,537; Pew Research Center") +
  labs (color = "Threat Level") +
  xlab ("Reported Family Income (USD)") +
  theme_bw()
```

```{r}
hchart(df_income, "line", hcaes(x = Var2, y = Freq, group = Var1))

```

How would you rate the job each of the following is doing responding to the coronavirus outbreak? 
- Donald Trump
```{r}
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

No Response -> Poor -> Fair -> Good -> Excellent

Spider chart

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
Analysis: More Repubilcans
```{r}
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```
