---
title: "mobility_questions"
author: "Nikhil Sharma"
date: "5/15/2020"
output: html_document
---

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(questionr)
library(highcharter)
options(scipen=999)
survey <- read_csv("CLEANED_SURVEY_64.csv")
```

```{r}
survey$F_IDEO_recode <- survey$F_IDEO %>% str_remove_all("Very")
```


```{r}
wtd.table(survey$F_IDEO_recode, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$F_PARTYSUM_FINAL, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

```{r}
wtd.table(survey$F_PARTYSUM_FINAL, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

```{r}
wtd.table(survey$F_INCOME_RECODE, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```


# elections
*************
How would you rate the job each of the following is doing responding to the coronavirus outbreak? 
- Donald Trump
Analysis: In general people think he has performed poorly
```{r}
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_IDEO_recode, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

80% dems think trump has done fairly or poorly

80% repubs think trump has done good or excellent

There is definite separation amongst the regions

Thinking about some steps that have been announced in some areas to address the coronavirus outbreak, in general do you think each of the
following have been necessary or unnecessary?
- Postponing upcoming state primary elections
Analysis: More democrats want to postpone, Less in west want to postpone, more younger people want to postpone
```{r}
wtd.table(survey$COVID_RESTRICTION_g_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_g_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_RESTRICTION_g_W64, y = survey$F_IDEO_recode, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```


72% of dems think it is necessary to postpone state primaries
65% of repubs think it is necessary to postpone state primaries

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
Going to a polling place to vote
Analysis: More Repubilcans
```{r}
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_IDEO_recode, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

70% of democrats are uncomfortable going to polling places
61% of republicans are uncomfortable with going to polling places



One spider plot showing %

**************************

# elections end

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Visiting with a close friend or family member at their home
Analysis: Democrats are less comfortable, young people more comfortable
```{r}
wtd.table(survey$F_CDIVISION, y = survey$COVID_COMFORT_a_W64, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2) 
```

D: I
R:

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Eating out in a restaurant
Analysis: More republicans are okay with it, more young people are okay with it
```{r}
wtd.table(survey$F_CDIVISION, y = survey$COVID_COMFORT_b_W64, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2) 
```

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Attending a crowded party
Analysis: Generally people aren't okay with it
```{r}
wtd.table(survey$COVID_COMFORT_c_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Going out to the grocery store
Analysis: More republicans are okay
```{r}
wtd.table(survey$COVID_COMFORT_d_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Given the current situation with the coronavirus outbreak, would you feel comfortable or uncomfortable doing each of the following?
- Going to a polling place to vote
Analysis: More Repubilcans
```{r}
wtd.table(survey$COVID_COMFORT_e_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

