---
title: "Pew Explore"
author: "Nikhil Sharma"
date: "5/13/2020"
output: html_document
---

```{r}
library(tidyverse)
library(questionr)
options(scipen=999)
setwd("~/Downloads")
survey <- read_csv("CLEANED_SURVEY_64.csv")
View(survey)
```

```{r}
colSums(is.na(survey))
```


```{r}
colnames(survey)
```

Has your personal life changed? dash this question

```{r}
wtd.table(survey$COVIDCHG_W64, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

```{r}
wtd.table(survey$COVIDCHG_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table()
```

F_CREGION, F_AGECAT, F_RACETHN, F_PARTYSUM_FINAL, F_INCOME_RECODE 



How has Donald Trump done responding to COVID?
```{r}
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Your state elected officials:
```{r}
wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_b_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Your local elected officials:
```{r}
wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_c_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Public Health Officials (like CDC):
```{r}
wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_d_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Ordinary ppl in your community:
```{r}
wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_e_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

The news media:
```{r}
wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_CREGION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_AGECAT, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_RACETHN, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)

wtd.table(survey$COVIDEGFP_f_W64, y = survey$F_INCOME_RECODE, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

**Look at dems and republicans here; a key key finding**


```{r}
wtd.table(survey$COVIDEGFP_a_W64, y = survey$F_PARTYSUM_FINAL, weights = survey$WEIGHT_W64) %>% prop.table()
```


```{r}
wtd.table(survey$F_PARTYSUM_FINAL, y = survey$F_CDIVISION, weights = survey$WEIGHT_W64) %>% prop.table(margin = 2)
```

Income vs party:
```{r}
wtd.table(survey$F_PARTYSUM_FINAL, survey$F_INCOME_RECODE, survey$WEIGHT_W64) %>% prop.table(margin=1)
```

```{r}

```


