---
title: "DataFest"
author: "Kevin Chen"
date: "May 11, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Mobilty Data

## Read Data
```{r}
library(readr)
library(tidyverse)

#read csv file
mobility_data <- read.csv("Mobility and Lockdown Data\\Global_Mobility_Report_2.csv")
names(mobility_data)
```


#filter United States Data

```{r}
mobility_us <- mobility_data %>% filter(country_region_code == "US")

#check NAs
summary(mobility_us)

#convert to date
mobility_us$date <- as.Date(mobility_us$date, "%Y-%m-%d")

#find months
mobility_us$month <- months(mobility_us$date)
```


#filter to March--May
```{r}
#mar to may
mobility_mar_may <- mobility_us %>% filter(month %in% c("March","April","May")) 

#select Residential
mobility_residential <- mobility_mar_may %>% filter(sub_region_2 =="" & sub_region_1 != "")

#select relevant columns
mobility_mar_may <- mobility_mar_may[,c(1:7,9,10,12)] 

#mean change in movement categories visits by state
#each row of mobility us data reprsents a day 
mobility_summaries <- mobility_mar_may %>% 
  filter(sub_region_2 =="" & sub_region_1 != "") %>% #filter out general US observations and county observations
  group_by(sub_region_1) %>% summarise( Total_State_Observations = n(),
                                                      Grocery = mean(grocery_and_pharmacy_percent_change_from_baseline, na.rm = TRUE),
                                                      Grocery_NA = sum(is.na(grocery_and_pharmacy_percent_change_from_baseline))*100/n(),
                                                      Retail_and_Rec = mean(retail_and_recreation_percent_change_from_baseline, na.rm = TRUE),
                                                      Retail_NA = sum(is.na(retail_and_recreation_percent_change_from_baseline))*100/n(),
                                                      Workplace = mean(workplaces_percent_change_from_baseline, na.rm = TRUE),
                                                      Workplace_NA = sum(is.na(workplaces_percent_change_from_baseline))*100/n(),
                                                      Transit = mean(transit_stations_percent_change_from_baseline, na.rm = TRUE),
                                                      Transit_NA = sum(is.na(transit_stations_percent_change_from_baseline))*100/n())


write.csv(mobility_summaries, file = "mobility_summaries.csv")
```

#States and Regions
```{r}
states <- mobility_summaries$sub_region_1 %>% as.character()
region <- c("South", "West", "West", "South", "West", "West", "Northeast", "South", "South", "South", "South", "West", "West", "Midwest", "Midwest", "Midwest", "Midwest", "South", "South", "Northeast", "South", "Northeast", "Midwest", "Midwest", "South", "Midwest", "West", "Midwest", "West", "Northeast", "Northeast", "West", "Northeast", "South", "Midwest", "Midwest", "South", "West", "Northeast", "Northeast", "South", "Midwest", "South", "South", "West", "Northeast", "South", "West", "South", "Midwest","West")
region_df <- data.frame(States = states, Region = region)
```


#States and Subdivisions
```{r}
division <- c("East South Central", "Pacific", "Mountain", "West South Central", "Pacific", "Mountain", "New England", "South Atlantic", "South Atlantic","South Atlantic", "South Atlantic", "Pacific", "Mountain", "East North Central","East North Central", "West North Central", "West North Central", "East South Central", "West South Central","New England", "South Atlantic", "New England", "East North Central","West North Central" ,"East South Central", "West North Central", "Mountain", "West North Central", "Mountain", "New England","Middle Atlantic", "Mountain", "Middle Atlantic", "South Atlantic","West North Central","East North Central", "West South Central", "Pacific", "Middle Atlantic", "New England", "South Atlantic", "West North Central", "East South Central","West South Central","Mountain","New England", "South Atlantic", "Pacific","South Atlantic","East North Central", "Mountain")
divisions_df <- data.frame(state = states, division = division)
```


#Read Lockdown Dates Data
```{r}
lockdown_dates <- read.csv("lockdown_us.csv")

#filter out county lockdown dates
lockdown_dates <- lockdown_dates %>% filter(County == "")
```

#Merge Lockdown and Mobility Data
```{r}
#filter out general US obsservations ans county observations
mobility_mar_may <- mobility_mar_may %>% filter(sub_region_1 != "" & sub_region_2 == "") 

#change names and eliminate country columns
mobility_mar_may$country_region_code <- NULL
mobility_mar_may$country_region <- NULL
mobility_mar_may$sub_region_2 <- NULL


summary(mobility_mar_may)
#change sub_region_1 to State
names(mobility_mar_may)[1] <- "State" 

#join mobility data with lockdown dates
mobility_and_lockdown <- left_join(mobility_mar_may, lockdown_dates, by = c("State" = "State")) 

#drop country and county columns
mobility_and_lockdown$Country <- NULL
mobility_and_lockdown$County <- NULL

#rename lockdown dat and type cloumns
mobility_and_lockdown <- mobility_and_lockdown %>% rename(Lockdown_Date = Date,                                                           Lockdown_Type = Type)

#reorder df
mobility_and_lockdown <- mobility_and_lockdown %>% select(State, date, month, Lockdown_Date, Lockdown_Type, everything())

#convert lockdown date to character
mobility_and_lockdown$Lockdown_Date <- mobility_and_lockdown$Lockdown_Date %>% as.character() 

#convert lockdown date to date format
mobility_and_lockdown$Lockdown_Date <- mobility_and_lockdown$Lockdown_Date %>% as.Date("%Y-%m-%d")

```

#Lockdown lifted
```{r}
lifted_states <- c("Alabama", "Alaska", "Arkansas", "Colorado", "Florida", "Georgia", "Idaho", "Indiana", "Iowa", "Kansas", "Mississippi", "Missouri", "Montana", "Nebraska","Nevada","North Dakota","Oklahoma",  "Rhode Island", "South Carolina","South Dakota", "Tennessee", "Texas", "Utah", "West Virginia", "Wyoming")

lifted_dates <- c("2020-04-30","2020-04-24", NA, "2020-04-26","2020-05-04","2020-04-30","2020-04-30","2020-05-04",NA,"2020-05-03", "2020-04-27", "2020-05-03", "2020-04-26", NA, "2020-05-09",NA, NA, "2020-05-08", "2020-05-04",NA, "2020-04-30", "2020-04-30", NA, "2020-05-03", NA)

lifted_lockdown <- data.frame(lifted_states = lifted_states, lifted_dates = lifted_dates)

lifted_lockdown$lifted_dates <- as.Date(lifted_lockdown$lifted_dates, "%Y-%m-%d")
```

#Merge Residential, lockdown, and lockdown lifted
```{r}
residential_df <- left_join(mobility_residential, lockdown_dates, by = c("sub_region_1" = "State"))
residential_df <- left_join(residential_df, lifted_lockdown, by = c("sub_region_1" = "lifted_states"))
residential_df$Date <- residential_df$Date %>% as.Date("%Y-%m-%d")
residential_df_prelockdown <- residential_df %>% filter(date <= Date)
residential_df_prelockdown <- inner_join(residential_df_prelockdown, divisions_df, by = c("sub_region_1" = "state"))
residential_df_prelockdown <- residential_df_prelockdown %>% group_by(division) %>% summarise(Residential_Change_Before = mean(residential_percent_change_from_baseline, na.rm = TRUE)) 

residential_df_lockdown <- residential_df %>% filter((date > Date & date < lifted_dates) | (date > Date & is.na(lifted_dates)))
residential_df_lockdown <- inner_join(residential_df_lockdown, divisions_df, by = c("sub_region_1" = "state"))
residential_df_lockdown <- residential_df_lockdown %>% group_by(division) %>% summarise(Residential_Change_During = mean(residential_percent_change_from_baseline))

residential_df_postlockdown <- residential_df %>% filter(date> lifted_dates)
residential_df_postlockdown <- inner_join(residential_df_postlockdown, divisions_df, by = c("sub_region_1" = "state"))
residential_df_postlockdown <- residential_df_postlockdown %>% group_by(division) %>% summarise(Residential_Change_After = mean(residential_percent_change_from_baseline))
residential_df_merged <- inner_join(residential_df_prelockdown, residential_df_lockdown, by = c("division" = "division"))
residential_df_merged <- inner_join(residential_df_merged, residential_df_postlockdown, by = c("division" = "division"))
residential_df_merged %>% View()
```




#Merge mobility, lockdown, and lockdown lifted
```{r}
final_df <- left_join(mobility_and_lockdown, lifted_lockdown, by = c("State" = "lifted_states"))

#reorder columns
final_df <- final_df %>% select(State, date, month, Lockdown_Date, Lockdown_Type, lifted_dates, everything())
```

#Merge Region and Mobility
```{r}
final_df <- inner_join(final_df, region_df, by = c("State" = "States"))
final_df <- final_df %>% select(State, Region, everything())


#get lockdown states that have not reopened
perma_lockdown <- final_df %>% filter(!is.na(Lockdown_Date) & is.na(lifted_dates))

#get states tat never had lockdown
no_lockdown <- final_df %>% filter(is.na(Lockdown_Date))
no_lockdown
```

#Analysis before Lockdown by State
```{r}
pre_lockdown <- final_df %>% 
      filter(date <= Lockdown_Date) %>% 
      group_by(State) %>% 
      summarise(Grocery = mean(grocery_and_pharmacy_percent_change_from_baseline, na.rm = TRUE),
                                                      Grocery_NA = sum(is.na(grocery_and_pharmacy_percent_change_from_baseline))*100/n(),
                                                      Retail_and_Rec = mean(retail_and_recreation_percent_change_from_baseline, na.rm = TRUE),
                                                      Retail_NA = sum(is.na(retail_and_recreation_percent_change_from_baseline))*100/n(),
                                                      Workplace = mean(workplaces_percent_change_from_baseline, na.rm = TRUE),
                                                      Workplace_NA = sum(is.na(workplaces_percent_change_from_baseline))*100/n(),
                                                      Transit = mean(transit_stations_percent_change_from_baseline, na.rm = TRUE),
                                                      Transit_NA = sum(is.na(transit_stations_percent_change_from_baseline))*100/n())
a <- inner_join(pre_lockdown, region_df, by = c("State" = "States")) %>% filter(Region == "West") 
sum(a$Workplace)/nrow(a)
```

#Analysis during Lockdown by State
```{r}
lockdown <- final_df %>% #states which had lockdown that were then lifted
            filter(date > Lockdown_Date & date < lifted_dates) %>% 
            group_by(State) %>%
            summarise(Grocery = mean(grocery_and_pharmacy_percent_change_from_baseline, na.rm = TRUE),
                                                      Grocery_NA = sum(is.na(grocery_and_pharmacy_percent_change_from_baseline))*100/n(),
                                                      Retail_and_Rec = mean(retail_and_recreation_percent_change_from_baseline, na.rm = TRUE),
                                                      Retail_NA = sum(is.na(retail_and_recreation_percent_change_from_baseline))*100/n(),
                                                      Workplace = mean(workplaces_percent_change_from_baseline, na.rm = TRUE),
                                                      Workplace_NA = sum(is.na(workplaces_percent_change_from_baseline))*100/n(),
                                                      Transit = mean(transit_stations_percent_change_from_baseline, na.rm = TRUE),
                                                      Transit_NA = sum(is.na(transit_stations_percent_change_from_baseline))*100/n())
lockdown
```

#Analysis after Lockdown by State
```{r}
post_lockdown <- final_df %>% #states which had lockdown that were then lifted
            filter(date > lifted_dates) %>% 
            group_by(State) %>%
            summarise(Grocery = mean(grocery_and_pharmacy_percent_change_from_baseline, na.rm = TRUE),
                                                      Grocery_NA = sum(is.na(grocery_and_pharmacy_percent_change_from_baseline))*100/n(),
                                                      Retail_and_Rec = mean(retail_and_recreation_percent_change_from_baseline, na.rm = TRUE),
                                                      Retail_NA = sum(is.na(retail_and_recreation_percent_change_from_baseline))*100/n(),
                                                      Workplace = mean(workplaces_percent_change_from_baseline, na.rm = TRUE),
                                                      Workplace_NA = sum(is.na(workplaces_percent_change_from_baseline))*100/n(),
                                                      Transit = mean(transit_stations_percent_change_from_baseline, na.rm = TRUE),
                                                      Transit_NA = sum(is.na(transit_stations_percent_change_from_baseline))*100/n())
post_lockdown
```

#Analysis before lockdown by Region
```{r}
region_pre_lockdown <- inner_join(pre_lockdown, region_df, by = c("State" = "States"))
region_pre_lockdown %>% group_by(Region) %>% summarise(Grocery = mean(Grocery),
                                                       Retail_and_Rec = mean(Retail_and_Rec),
                                                       Workplace = mean(Workplace),
                                                       Transit = mean(Transit))
```

#Analysis during lockdown by Region
```{r}
region_lockdown <- inner_join(lockdown, region_df, by = c("State" = "States"))
region_lockdown %>% group_by(Region) %>% summarise(Grocery = mean(Grocery),
                                                       Retail_and_Rec = mean(Retail_and_Rec),
                                                       Workplace = mean(Workplace),
                                                       Transit = mean(Transit)) 
```

#Analysis post-lockown by region
```{r}
region_lockdown <- inner_join(post_lockdown, region_df, by = c("State" = "States"))
region_lockdown %>% group_by(Region) %>% summarise(Grocery = mean(Grocery),
                                                       Retail_and_Rec = mean(Retail_and_Rec),
                                                       Workplace = mean(Workplace),
                                                       Transit = mean(Transit)) 

```

#Average movement change before lockdown by state
```{r}
pre_lockdown %>% mutate(Avg_Movement = (Grocery + Retail_and_Rec + Workplace + Transit)/4) %>% select(State, Avg_Movement) %>% arrange(Avg_Movement)
```

#Average movement change during lockdown by state
```{r}
lockdown %>% mutate(Avg_Movement = (Grocery + Retail_and_Rec + Workplace + Transit)/4) %>% select(State, Avg_Movement) %>% arrange(Avg_Movement)
```

#Average movement change after lockdown ended
```{r}
post_lockdown %>% mutate(Avg_Movement = (Grocery + Retail_and_Rec + Workplace + Transit)/4) %>% select(State, Avg_Movement) %>% arrange(Avg_Movement)
```


#Movement change by groceries before lockdown
```{r}
pre_lockdown_grocery <- pre_lockdown %>% select(State, Grocery) %>% arrange(Grocery)
pre_lockdown_grocery
```

#Movement change by groceries during lockdown
```{r}
lockdown_grocery <- lockdown %>% select(State, Grocery) %>% arrange(Grocery)
lockdown_grocery
```

#Movement change by groceries after lockdown
```{r}
post_lockdown_grocery <- post_lockdown %>% select(State, Grocery) %>% arrange(Grocery)
post_lockdown_grocery

```

#Movement change by recreation before lockdown
```{r}
pre_lockdown_recreation <- pre_lockdown %>% select(State, Retail_and_Rec) %>% arrange(Retail_and_Rec)
pre_lockdown_recreation
```

#Movement change by recreation during lockdown
```{r}
lockdown_recreation <- lockdown %>% select(State, Retail_and_Rec) %>% arrange(Retail_and_Rec)
lockdown_recreation
```

#Movement change by recreation after lockdown
```{r}
post_lockdown_recreation <- post_lockdown %>% select(State, Retail_and_Rec) %>% arrange(Retail_and_Rec)
post_lockdown_recreation
```

#Movement change by workplace before lockdown
```{r}
pre_lockdown_workplace <- pre_lockdown %>% select(State, Workplace) %>% arrange(Workplace)
pre_lockdown_workplace
```

#Movement change by workplace during lockdown
```{r}
lockdown_workplace <- lockdown %>% select(State, Workplace) %>% arrange(Workplace)
lockdown_workplace
```

#Movement change by workplace after lockdown
```{r}
post_lockdown_workplace <- post_lockdown %>% select(State, Workplace) %>% arrange(Workplace)
post_lockdown_workplace
```

#Movement change by transit before lockdown
```{r}
#pre_lockdown <- 
```

#grocery change by division before lockdown
```{r}
#pre lockdown data merged with state divisions
pre_lockdown_div <- inner_join(pre_lockdown, divisions_df, by = c("State" = "state"))

pre_lockdown_grocery <- pre_lockdown_div %>% group_by(division) %>% summarise(Grocery_Change = mean(Grocery)) %>% arrange(Grocery_Change)
```

#recreation change by division before lockdown
```{r}

pre_lockdown_recreation <- pre_lockdown_div %>% group_by(division) %>% summarise(Recreation_Change = mean(Retail_and_Rec))
pre_lockdown_recreation <- pre_lockdown_recreation %>% arrange(Recreation_Change)
pre_lockdown_recreation
```

#workplace change by division before lockdown
```{r}
pre_lockdown_workplace <- pre_lockdown_div %>% group_by(division) %>% summarise(Workplace_Change = mean(Workplace)) %>% arrange(Workplace_Change)
pre_lockdown_workplace
```

#transit change by division before lockdown
```{r}
pre_lockdown_transit <- pre_lockdown_div %>% group_by(division) %>% summarise(Transit_Change = mean(Transit)) %>% arrange(Transit_Change)
pre_lockdown_transit
```

#Lockdown states: merge states with lifted lockdown and ongoing lockdown 
```{r}
#states with only lockdown
perma_lockdown_2 <- perma_lockdown %>% group_by(State) %>% summarise(Grocery = mean(grocery_and_pharmacy_percent_change_from_baseline),
                                                                     Retail = mean(retail_and_recreation_percent_change_from_baseline),
                                                                     Workplace = mean(workplaces_percent_change_from_baseline),
                                                                     Transit = mean(transit_stations_percent_change_from_baseline))

#merge with divisions
perma_lockdown_2 <- inner_join(perma_lockdown_2, divisions_df, by = c("State" = "state"))
lockdown <- inner_join(lockdown, divisions_df, by = c("State" = "state"))

#remove % NA columns from lockdown df
lockdown <- lockdown %>% select(State, division, Grocery, Retail_and_Rec, Workplace, Transit) %>% rename(Division = division)

#rename perma lockdown columns
perma_lockdown_2 <- perma_lockdown_2 %>% rename(Division = division, Retail_and_Rec = Retail)

#row bind perma lockdown and temp lockdown states
lockdown_2 <- bind_rows(lockdown, perma_lockdown_2)
```

#Grocery change by division during lockdown
```{r}
lockdown_2_grocery <- lockdown_2 %>% group_by(Division) %>% summarise(Grocery_Change = mean(Grocery)) %>% arrange(Grocery_Change)
```

#Retail change by division during lockdown
```{r}
lockdown_2_retail <- lockdown_2 %>% group_by(Division) %>% summarise(Retail_Change = mean(Retail_and_Rec)) %>% arrange(Retail_Change)
lockdown_2_retail
```

#Workplace change by division during lockdown
```{r}
lockdown_2_workplace <- lockdown_2 %>% group_by(Division)%>% summarise(Workplace_Change = mean(Workplace)) %>% arrange(Workplace_Change)
```

#Transit change by division during lockdown
```{r}
lockdown_2_transit <- lockdown_2 %>% group_by(Division) %>% summarise(Transit_Change = mean(Transit)) %>% arrange(Transit_Change)
```

#Grocery change by division after lockdown
```{r}
#Merge division and post lockdown data
post_lockdown <- inner_join(post_lockdown, divisions_df, by = c("State" = "state"))

post_lockdown_2 <- post_lockdown %>% group_by(division) %>% summarise(Grocery_Change = mean(Grocery),
                                                                      Retail_Change = mean(Retail_and_Rec, na.rm = TRUE),
                                                                      Workplace = mean(Workplace),
                                                                      Transit = mean(Transit))

post_lockdown_grocery <- post_lockdown_2 %>% select(division, Grocery_Change) %>% arrange(Grocery_Change)
post_lockdown_grocery
```

#Retail change by division after lockdown
```{r}
post_lockdown_recreation <- post_lockdown_2 %>% select(division, Retail_Change) %>% arrange(Retail_Change)
post_lockdown_recreation <- post_lockdown_recreation %>% rename(Recreation_Change = Retail_Change)
post_lockdown_recreation 
```

#Transit change by division after lockdown
```{r}
post_lockdown_transit <- post_lockdown_2 %>% select(division, Transit) %>% rename(Transit_Change = Transit) %>% arrange(Transit_Change)
post_lockdown_transit
```

#Workplace change by division after lockdown
```{r}
post_lockdown_workplace <- post_lockdown_2 %>% select(division, Workplace) %>% rename(Workplace_Change = Workplace) %>% arrange(Workplace_Change)
post_lockdown_workplace

```

#Merged Grocery Change
```{r}
grocery_merged <- left_join(pre_lockdown_grocery, lockdown_2_grocery, by= c("division" = "Division"))
grocery_merged <- grocery_merged %>% rename(Grocery_Change_Before = Grocery_Change.x, Grocery_Change_During = Grocery_Change.y )
grocery_merged <- left_join(grocery_merged, post_lockdown_grocery, by = c("division" = "division")) 
grocery_merged <- grocery_merged %>% rename(Grocery_Change_After = Grocery_Change)
grocery_merged %>% mutate(During_vs_Before = Grocery_Change_During - Grocery_Change_Before, After_vs_During = Grocery_Change_After - Grocery_Change_During) %>% View()
grocery_merged %>% write.csv(file = "grocery_merged.csv")
```

#Merged Recreation Change
```{r}
recreation_merged <- left_join(pre_lockdown_recreation , lockdown_2_retail, by = c("division" = "Division")) 
recreation_merged <- recreation_merged %>% rename(Recreation_Change_Before = Recreation_Change, Recreation_Change_During = Retail_Change)
recreation_merged <- left_join(recreation_merged, post_lockdown_recreation, by = c("division" = "division")) %>% rename(Recreation_Change_After = Recreation_Change)
recreation_merged %>% arrange(Recreation_Change_Before)
recreation_merged %>% arrange(Recreation_Change_During)
recreation_merged %>% write.csv(file = "recreation_merged.csv")
```



#Merged Workplace Change
```{r}
merged_workplace <- left_join(pre_lockdown_workplace, lockdown_2_workplace, by = c("division" = "Division"))
merged_workplace <- merged_workplace %>% rename(Workplace_Change_Before = Workplace_Change.x, Workplace_Change_During = Workplace_Change.y)
merged_workplace <- left_join(merged_workplace, post_lockdown_workplace, by = c("division" = "division")) %>% rename(Workplace_Change_After = Workplace_Change)
merged_workplace %>% write.csv(file = "merged_workplace.csv")
```

#Merged Transit Change
```{r}
merged_transit <- left_join(pre_lockdown_transit, lockdown_2_transit, by = c("division" = "Division"))
merged_transit <- merged_transit %>% rename(Transit_Change_Before = Transit_Change.x, Transit_Change_During = Transit_Change.y)
merged_transit <- left_join(merged_transit, post_lockdown_transit, by = c("division" = "division")) %>% rename(Transit_Change_After = Transit_Change)
merged_transit %>% write.csv(file = "merged_transit.csv")

write.csv(residential_df_merged, file = "residential_merged.csv")
```

#usmap to chart mobility

```{r}
library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)
```

1. Residential


```{r}
usa <- map_data("usa")

```

